Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-28 tex/ms.tex
more figures and more text tweaks

@@

The data we use to test our method consist of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-9100 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  {\color{blue} Wavelength
calibration happened. Sky subtraction happened.} The data were
approximately spectrophotometrically calibrated using an average
calibration vector for the night constructed from {\color{blue} MORE
HERE}. Figure \ref{fig:data} shows the spectra before and after
calibration {\color{blue} SHOULD THIS SHOW ALL THE CLUSTERS OR JUST ONE?.  Discuss
S/N, sky subtraction.}

{\color{red} Specify order of calibration polynomial here?}

\begin{figure*}[h!]
\includegraphics[width = \textwidth]{figures/dfig_b192-g242_020.png}
\caption{The calibrated (left) and uncalibrated (right) spectrum for
  \excluster, along with the uncertainties (bottom panel). The
  spectra are not normalized. \label{fig:data}}
\end{figure*}

@@

Our prior distributions are in all cases top-hat functions, though
more informative prior distributions may be used.  Informative priors
may be especially appropriate for the calibration parameters $\alpha$
if additional information about the instrument is available; or for the
parameters of interest $\theta$, for example in the case that there
is knowledge of the metallicity distribution of the population from
which a given cluster is drawn.

\input{tables/priors.tbl}
\subsection{Results}

@@

\begin{figure}[h!]
\caption{Show a corner plot of selected relevant parameters, for one
cluster. \label{fig:inferred_params}}
\end{figure}

@@

\acknowledgements
Thanks to X. for bringing us beer.

>>>>

\begin{figure}[h!]
\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
\caption{The calibrated (left) and uncalibrated (right) spectrum for
\excluster, along with the uncertainties (bottom panel). The spectra
have been renormalized to avoid floating point errors. {\color{blue}
SHOULD THIS SHOW ALL THE CLUSTERS OR JUST ONE?.}\label{fig:data}}
\end{figure}

@@

The data we use to test our method consist of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-9100 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  {\color{blue} Wavelength
calibration happened. Sky subtraction happened.} The data were
approximately spectrophotometrically calibrated using an average
calibration vector for the night constructed from {\color{blue} MORE
HERE. Discuss S/N, sky subtraction.}

An example spectrum, both after and before spectrophotometric
calibration, is shown in Figure \ref{fig:data}.  When fitting the
spectra we mask the region around the bright OI5577 sky line, and we
fit only to the spectrum with $3750 < \lambda < 7200$ to avoid the low
S/N edges and, on the red side, imperfect sky line subtraction in a
region of the spectrum that has a paucity of informative spectral
lines.Furthermore, the MILES empirical spectra (see
\S\ref{sec:cluster_model}) are only available for $\lambda < 7500$\AA
{\color{red} Specify/Justify order of calibration polynomial here?}.

@@

Our prior distributions are in all cases top-hat functions, described
in Table \ref{tbl:priors}, though more informative prior distributions
may be used.  Informative priors may be especially appropriate for the
calibration parameters $\alpha$ if additional information about the
instrument is available; or for the parameters of interest $\theta$,
for example in the case that there is knowledge of the metallicity
distribution of the population from which a given cluster is drawn.

\input{tables/priors.tbl}

\subsection{Results}

@@

\begin{figure}[h!]
\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_020_cal.png}
\caption{ Marginalized and joint PDFs of  subset of the physical
  parameters $\theta$ inferred from the spectophotometrically
  calibrated spectrum of \excluster. \label{fig:inferred_params}}
\end{figure}

@@

\acknowledgements
Thanks to X. for bringing us beer.
DRW is supported by NASA through Hubble Fellowship grant
  HST-HF-51331.01 awarded by the Space Telescope Science Institute.
BDJ and DRW acknowledge the hospitality of Hans-Walter Rix and the MPIA. 
CC is supported by Packard and Sloan Foundation Fellowships. 
This research made extensive use of NASA's Astrophysics Data System Bibliographic Services. 
In large part, analysis and plots presented in this paper utilized
  iPython and packages from NumPy, SciPy, and Matplotlib
  \citep[][]{hunter2007, oliphant2007, perez2007, astropy2013} as well
  as python-FSPS  (http:://github.com/dfm/python-fsps) .
